---
title: "R Session 1S"
output: html_notebook
---

# 1. Descriptive Statistics

### 1.1 Load and view data
```{r}
library(MASS)
View(quine)
```

### 1.2 Mean and median:
Use the variable Days in quine
```{r}
# please input here...
mean(quine$Days)
median(quine$Days)
```

### 1.3 Mode:
Use the variable Eth in quine
```{r}
getmode <- function(x){
    ux <- unique(x)
    ux[which.max(tabulate(match(x, ux)))]
  }
# please input here...
getmode(quine$Eth)
```

### 1.4 Geometric mean:
Use any vector
```{r}
install.packages("psych")
library(psych)
# please input here...
geometric.mean(c(0.5, 2))
```

### 1.5 Range, variance and standard deviation:
Use the variable Days in quine
```{r}
# please input here...
range(quine$Days)
var(quine$Days)
sd(quine$Days)
```

### 1.6 Coefficient of variation (CV):
Use the variable Days in quine
```{r}
# please input here...
sd(quine$Days) / mean(quine$Days) * 100
```


### 1.7 Z-score:
Use the variable Days in quine
```{r}
# please input here...
x <- 15
(x - mean(quine$Days)) / sd(quine$Days)
```

### 1.8 Skewness and kurtosis:
Use the variable Days in quine
```{r}
install.packages("moments")
library(moments)
# please input here...
skewness(quine$Days)
kurtosis(quine$Days)
```

### 1.9 Quartile:
Use the variable Days in quine
```{r}
# please input here...
quantile(quine$Days)
quantile(quine$Days, probs=c(0.1, 0.2, 0.5))
quantile(quine$Days, probs=seq(0, 1, by=0.1))
```

### 1.10 Five-number summary:
Use the variable Days in quine
```{r}
# please input here...
summary(quine$Days)
summary(quine)
```

### 1.11 Boxplot:
Use the variable Days in quine
```{r}
# please input here...
boxplot(quine$Days, horizontal=TRUE)
boxplot(quine$Days, horizontal=TRUE, range=0)
```


# 2. Normal Distributions

### 2.1 Probability density function
```{r}
# please input here...
x <- seq(-5, 5, by=0.1)
y <- dnorm(x)
plot(x, y)
```

### 2.2 Cumulative distribution function
```{r}
# please input here...
x <- seq(-5, 5, by=0.1)
y <- pnorm(x)
plot(x, y)
```

### 2.3 Quantile function
```{r}
# please input here...
x <- seq(0, 1, by=0.01)
y <- qnorm(x)
plot(x, y)
```

### 2.4 Random number generator
```{r}
# please input here...
x <- rnorm(10000)
hist(x, breaks=30)
```

# 3. Confidence Interval

### 3.1 Z distribution for population mean:
```{r}
# please input here...
n <- 11           # sample size
xbar <- 2.2       # sample mean
sigma <- 0.35     # population std
alpha <- 1-0.95   # confidence level
z_value <- abs(qnorm(alpha/2)) # z value
conf_intv <- c(xbar - z_value*sigma/sqrt(n),
xbar+z_value*sigma/sqrt(n))
conf_intv
```

### 3.2 T distribution for population mean:
```{r}
# please input here...
n <- 25
xbar <- 50
s <- 8
alpha <- 1-0.95
t_value <- abs(qt(alpha/2, df=n-1))
t_value
conf_intv <- c(xbar - t_value*s/sqrt(n),
xbar + t_value*s/sqrt(n))
conf_intv
```

### 3.3 Z distribution for population proportion:
```{r}
# please input here...
n <- 100
p <- 25/n
alpha <- 1-0.95
z_value <- abs(qnorm(alpha/2))
z_value
conf_intv <- c(p - z_value*sqrt(p*(1-p)/n),
p + z_value*sqrt(p*(1-p)/n))
conf_intv

```

### 3.4 Confidence interval function:
```{r}
# please input here...
install.packages("Rmisc")
library(Rmisc)

x <- c(1.44, -0.93, 0.54, 1.28, -0.52)
conf_intv <- CI(x, ci=0.95)
conf_intv
```
